Ensemble Methods for Robust Feature Selection

### 2016-08-02 paper/paper.tex
robustness of the different combinations

Symmetrical Uncertainty \citep{press1996numerical} is entropy based measurement. It is the normalized mutual information between the feature and the class. The mutual information measures the influence of the knowledge of the class on the feature value in terms of entropy and normalizes it. More details about mutual information can be found in \cite{paninski2003estimation}.
\begin{equation}
  \label{eq:su}
  SU(F,C) = 2 \frac{H(F) - H(F|C)}{H(F) + H(C)} \textrm{, where } H(\cdot) \textrm{ is the entropy.}
\end{equation}

@@

\begin{description}[align=left]
\item [Linear aggregation :] The average of the weights was taken as the new weight.
\item [Non-linear aggregation :] Two methods were used, first averaging powers of the weights and secondly aggregating linearly the minimum, maximum and the average of the weights.
\item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers. The feature selection methods result were weighted accordingly to their accuracy.
\end{description}

@@

>>>>

Symmetrical Uncertainty (SU) \citep{press1996numerical} is entropy based measurement. It is the normalized mutual information between the feature and the class. The mutual information measures the influence of the knowledge of the class on the feature value in terms of entropy and normalizes it. More details about mutual information can be found in \cite{paninski2003estimation}.
\begin{equation}
  \label{eq:su}
  SU(F,C) = 2 \frac{H(F) - H(F|C)}{H(F) + H(C)} \textrm{, where } H(\cdot) \textrm{ is the entropy.}
\end{equation}

@@

\begin{description}[align=left]
\item [Linear aggregation :] The average of the weights was taken as the new weight. Two version were used, one where a normalization of the weight sum is applied and the other without it.
\item [Non-linear aggregation :] To emphasize features with importance, the weights are non-linearly transformed with the equation \ref{eq:em_non_linear}. $\arctan$ in in combination with $\exp$ to considerably shrink the low weights. Finally the weights sum is normalized.

\begin{equation}
  \label{eq:em_non_linear}
  W_i = \frac{f \left( W_i \right)}{\sum_k f \left( W_k \right)} \quad with \quad f : x \rightarrow \exp( \arctan(x - 1) )
\end{equation}

\item [Performance related aggregation :] For each feature selector the best 1\% of the features were selected and used to measure the classification performance for multiple classifiers. The feature selection methods result were weighted accordingly to their accuracy. It was used in combination with the precedent ensemble methods.
\end{description}

@@

\subsubsection{Different combinations of feature selectors}
The presented ensemble methods were used with all possible combinations of feature selectors. For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset. While the accuracy does not change considerably with the different combinations, the robustness is heavily affected by the presence or not of the feature selector Lasso as can be seen in the figure \ref{fig:combination_robustness}. This is due to the low robustness of the feature selector Lasso itself. On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.

\begin{figure}
\centering \includegraphics[]{images/Robustness_of_the_different_combinations.pdf}
\caption{Robustness of the different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
\label{fig:combination_robustness}
\end{figure}
